Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-02-28 Thesis/chapter/03-theoretical-background.tex
renamed chapter with numbers

%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\subsection{Sputtering}
%https://en.wikipedia.org/wiki/Sputter_deposition
\subsection{SEM}
\url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
\subsection{Infrared absorption}
\td{IR around page 45;
REFLECTIVITY? can also be used for determination of thickness p47
}
\subsection{X-Ray Diffraction}
\url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
\url{https://chem.libretexts.org/Courses/Franklin_and_Marshall_College/Introduction_to_Materials_Characterization__CHM_412_Collaborative_Text/Diffraction_Techniques/X-ray_diffraction_(XRD)_basics_and_application}\\
\subsection{Particle Swarm Optimization}
\subsection{Machine Learning}
\subsubsection{History}
\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
\subsection{Princlipal Component Analysis}
reinforcement learning could also have been a nice option

>>>>

%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\todo{Structure: Free writing} 
Ueber das Material, also PV und speziell CIGS (copper indium gallium sulfide) 
ueber den MC prozess berichten, also DB, i-v curven, sputtering, sem, ir, xrd
ueber den it ml stuff und statistisch, also ML algemein, pso im speziellen 
perfekt fuer intro einfach mal erwaehnen was wo in diesem capitel zu finden sein wird. 
Books PV, analytic otto? 
\subsection{Photovoltaik and CSGI}
The grundlage for all pvs is the photovoltaik effect which was entdeckt by Albert Einstein adn for which he got the nobel price. 
The Prinziple is easy: When the energy (E = hv) of the light is \td{large,strong,big,high}er than the binding energy of an electron the electron is ejected with the remaining energy as kinetic energy 
\begin{math}
	E_{kin}=hv - Eb
\end{math}
Different Materials have different binding energies. Metalls do have in general lower binding energies than covalent bound material and halbleiter do have even lowers E_b. 
Thats Silica is in a lot of PVs. 
The next generation of PVs. 
CIGS has in contrast to silicium based PV a direct band gap\td{source and what does that mean?}
duennschicht pv, haben eine effeftivitaet von 7-16\% vs 15-22\% \cite{Mertens2018}
\subsection{Zirconium oxide}
\subsection{Sputtering}
%https://en.wikipedia.org/wiki/Sputter_deposition
\subsection{SEM}
\url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
\subsection{Infrared absorption}
\td{IR around page 45;
REFLECTIVITY? can also be used for determination of thickness p47
}
\subsection{X-Ray Diffraction}
\url{https://doi.org/10.1016/B978-0-12-816806-6.00017-0}\\
\url{https://chem.libretexts.org/Courses/Franklin_and_Marshall_College/Introduction_to_Materials_Characterization__CHM_412_Collaborative_Text/Diffraction_Techniques/X-ray_diffraction_(XRD)_basics_and_application}\\
\subsection{Particle Swarm Optimization}
\subsection{Machine Learning}
\subsubsection{History}
\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
\subsection{Princlipal Component Analysis}
reinforcement learning could also have been a nice option

### 2022-02-28 Thesis/chapter/04-experimental.tex
renamed chapter with numbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec:exp}
%\subsection{finding a solution}
%\subsection{finding process variables}
In this section the used chemicals and substrates, experimental procedures and any used 
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
The experiments can be split into three sections: 
In the first section the base recipe and the base process were sought. 
In the pre-optimisation section the boundaries for the optimisation were investigated. 
And during the third and final step the experiments for the optimisation were performed.
\subsection{Substrate Preparation}
Five different substrates were used throughout this work: 
microscope glass slides (\cm{2.5}\x\cm{7.5})\ds{ from Sigma Aldrich},\ds{ thinner,} squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squwares fo the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Solutions}
%Two main recipes were used and their compositions were varied. 
All recipes for solutions can be divided into two categories:
the first recipe - adopted from Anwar et. al. \cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water}.
The second recipe - adopted from Hu et. al. \cite{Hu2016} - was based on \gls{zrpro} in \gls{buoh}.

@@

\begin{table}[h]
	\centering
	\caption{}
	\label{tab:rec2}
	\begin{tabular}{rlllll}
		\hline
		recipe	&1F		&2F		&3F		&4F		&5F		\\
		\hline
		\gls{buoh} [\ml{}]		&4.95	&4.9	&4.85	&4.8	&4.75	\\
		\gls{zrpro} [\ml{}]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
		\gls{acac} [\ml{}]		&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
		\gls{ipo}/\gls{acoh} [\ml{}]		&2		&2		&2		&2		&2		\\
		\hline
	\end{tabular}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calcination}
A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate 
the doctor bladed samples. 
The heating plate could hold temperature for a certain amount of time, but heated with a 
fixed rate of circa \oc{10}/\minutes{}.
%The heating plate heated with a steady rate of \td{\oc{5}/\minutes{}}.
In order to achieve a lower overall heating rate several temperature ramps and plateaus 
were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
This procedure was called HP1.
The HP1 procedure was optimized for the available hardware by a colleague working on the 
project prior to the author.

\begin{table}[h]
	\centering
	%\caption{Time the temperature was held constant at certain temperatures on the heating plate}
    \caption{Heating programs}
    \subcaption{Heating program HP1 used with the Labtech EH45C heating plate}
	\label{tab:labtech}
	\begin{tabular}{rl ll ll ll ll ll ll }%ll ll ll ll ll ll ll}
		\hline
		\hline
		T [\oc{}]	    &80		&100	&150	&160	&170 	&180	&190	&200	&250	&300	&350	&400	\\
		t [\minutes{}]	&10 	&10		&5 		&5 		&5 		&5 &5 &10 &10 &10 &10 &60 \\
		\hline
		\hline
	\end{tabular}
%%%%%%%%%%%%
    \subcaption{Heating programs NT1 - NT6 used with the Naberterm LB410 muffle furnace}
	\label{tab:nt}
	\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
		\hline\hline
		Name	&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
		\hline
		NT1		&2					&1					&2				&400	&60  \\
		NT2		&2					&2					&2				&400	&60  \\
		NT3		&3					&3					&3				&400	&60  \\
		NT4		&4					&4					&4				&400	&60  \\
		NT5		&4					&4					&4				&500	&60  \\
		NT6		&1					&1					&1				&400	&60  \\
%		NT7		&max				&max				&max			&600	&60  \\
		\hline\hline
	\end{tabular}
\end{table}
%
%\clearpage
The NT1 heating program was used to mimic the HP1 heating procedure from the heating 
plate in the Naberterm muffle furnace. 
NT2 is an simplification of NT1 and programs NT3~-~NT6 are the same as NT2 with altered 
heating rate and 
NT5 additionally used a calcination temperature T$_{\textrm{Cal}}$ of \SI{500}{\celsius}.
NT2-NT6 had 2 variables (heating rate and calcination temperature) in contrast to 
NT1 which had 4 (three different heating rates and calcination temperature). 
All heating programs were held at the calcination temperature for one hour.
%In figure \ref{fig:heat} the different heating curves are depicted. 
%
%\begin{figure}
%	\centering
%	\includegraphics[width=.7\textwidth]{../Data/Graphs/hp1.png}
%	\caption{Different heatings curves}
%	\label{fig:heat}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Characterisation}
All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
\Gls{ft} \gls{ir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter} - \SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a Silicon detector for visual and \gls{ir} light 
(\SI{500}{\nano\meter} - \SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The UV and VIS+IR spectra were merged 
in Opus software. % included in the spectrometer. 
%\td{IR around page 45
%REFLECTIVITY? can also be used for determination of thickness p47
%}
\Gls{xrd} spectra were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.

The \gls{iv} curves were measured with Agilent 4156C Precision Semiconductor 
Parameter Analyzer from \SI{-0.5}{\volt} to \SI{0.5}{\volt} with steps of 
\SI{10}{\milli\volt}.
%
Prior to \gls{iv} measurements the samples were sputtered with aluminium 
through a mask to produce a multitude of equidistant contacts with a Leybold 
UNIVEX450C Sputter System.
%https://en.wikipedia.org/wiki/Sputter_deposition
Directional current sputtering was used with Argon as inert gas at \SI{0.005}{\milli\bar} 
and with a power of \SI{40}{\watt} for \SI{700}{\second}.
Between sputtering and \gls{iv} measurements 
direct contacts to the steel subtrate were created by removing the \gls{zro} layer with 
sand paper on two opposing edges of a sample and then by applying silver paste.
%\td{scratched until short circuit was produced (aka the steel foil was reached under the \gls{zro} layer).  }
See figure~\ref{fig:circuit} for a sketch of the connectivity.

@@

%\subsection{Preparatory Experiments/series (Pro-optimisation/Finding base process/Preliminary study)}

@@

The then current procedure produced clear and continuous films, but was plagued from 

@@

allowed to hold the sample in place through underpressure and heat it to a certain 

@@

relative concentration $conc$, number of layers $layers$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively. 
After testing the first samples, the \gls{db} velocities altered to 1 and 5 (see table \ref{tab:pre-opt1}).
\begin{table}[htb]

@@

@@

	conc	&layers	&$v_{\textrm{DB}}$	&$T_{\textrm{DB}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\

@@

	conc	&layers	&$v_{\textrm{DB}}$	&$T_{\textrm{DB}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\

@@

	4	&6	&14	&60	&240	&500	\\
	4	&6	&14	&60	&240	&500	\\
	4	&6	&14	&60	&240	&500	\\

@@

@@

	\caption{}

@@

%$T_{DB}$[\oc{}]
%$v_{DB}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a DB machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Shortly before the \gls{pso} the stabilisation agent was changed from \gls{acoh} to 
\gls{ipo} because of much better soltion stability.
After 
%a fitting recipe was found and 
the boundaries were fixed the process variables to 
produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
See table \ref{tab:space} for the space spanned for the optimisation.
\begin{table}[ht!]
    \caption{}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section the used chemicals and substrates, experimental procedures and any used 
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
The experiments can be split into three sections: 
In the first section the base recipe and the base process were sought. 
In the pre-optimisation section the boundaries for the optimisation were investigated. 
And during the third and final step the experiments for the optimisation were performed.
\subsection{Substrate Preparation}
Five different substrates were used throughout this work: 
microscope glass slides (\cm{2.5}\x\cm{7.5})\ds{ from Sigma Aldrich},\ds{ thinner,} squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, \gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squwares fo the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Solutions}
All recipes for solutions can be divided into two categories:
the first recipe - adopted from Anwar et. al. \cite{Anwar2017} - was based on \gls{zrpro} in \gls{acac} and \gls{water}.
The second recipe - adopted from Hu et. al. \cite{Hu2016} - was based on \gls{zrpro} in \gls{buoh}.

@@

\begin{table}[h]
	\centering
	\caption{Composition of different buthanolic solutions}
	\label{tab:rec2}
	\begin{tabular}{rlllll}
		\hline
		recipe	&1F		&2F		&3F		&4F		&5F		\\
		\hline
		\gls{buoh} [\ml{}]		&4.95	&4.9	&4.85	&4.8	&4.75	\\
		\gls{zrpro} [\ml{}]	&0.05	&0.1	&0.15	&0.2	&0.25	\\
		\gls{acac} [\ml{}]		&0.0125	&0.025	&0.0375	&0.05	&0.0625	\\
		\gls{ipo}/\gls{acoh} [\ml{}]		&2		&2		&2		&2		&2		\\
		\hline
	\end{tabular}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calcination}
A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate 
the doctor bladed samples. 
The heating plate could hold temperature for a certain amount of time, but heated with a 
fixed rate of circa \oc{10}/\minutes{}.
In order to achieve a lower overall heating rate several temperature ramps and plateaus 
were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
This procedure was called HP1.
The HP1 procedure was optimized for the available hardware by a colleague working on the 
project prior to the author.

\begin{table}[h]
	\centering
    \caption{Heating programs}
	\label{tab:heating}
    \subcaption{Heating program HP1 used with the Labtech EH45C heating plate}
	\label{tab:labtech}
	\begin{tabular}{rl ll ll ll ll ll ll }%ll ll ll ll ll ll ll}
		\hline
		\hline
		T [\oc{}]	    &80		&100	&150	&160	&170 	&180	&190	&200	&250	&300	&350	&400	\\
		t [\minutes{}]	&10 	&10		&5 		&5 		&5 		&5 &5 &10 &10 &10 &10 &60 \\
		\hline
		\hline
	\end{tabular}
%%%%%%%%%%%%
    \subcaption{Heating programs NT1 - NT6 used with the Naberterm LB410 muffle furnace}
	\label{tab:nt}
	\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
		\hline\hline
		Name	&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
		\hline
		NT1		&2					&1					&2				&400	&60  \\
		NT2		&2					&2					&2				&400	&60  \\
		NT3		&3					&3					&3				&400	&60  \\
		NT4		&4					&4					&4				&400	&60  \\
		NT5		&4					&4					&4				&500	&60  \\
		NT6		&1					&1					&1				&400	&60  \\
%		NT7		&max				&max				&max			&600	&60  \\
		\hline\hline
	\end{tabular}
\end{table}
%
%\clearpage
The NT1 heating program was used to mimic the HP1 heating procedure from the heating 
plate in the Naberterm muffle furnace. 
NT2 is an simplification of NT1 and programs NT3~-~NT6 are the same as NT2 with altered 
heating rate and 
NT5 additionally used a calcination temperature T$_{\textrm{Cal}}$ of \SI{500}{\celsius}.
NT2-NT6 had 2 variables (heating rate and calcination temperature) in contrast to 
NT1 which had 4 (three different heating rates and calcination temperature). 
All heating programs were held at the calcination temperature for one hour.
%In figure \ref{fig:heat} the different heating curves are depicted. 
%
%\begin{figure}
%	\centering
%	\includegraphics[width=.7\textwidth]{../Data/Graphs/hp1.png}
%	\caption{Different heatings curves}
%	\label{fig:heat}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Characterisation}
All \gls{sem} micrographs were taken with a Zeiss Supra 40. 
\Gls{ft} \gls{ir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter} - \SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a Silicon detector for visual and \gls{ir} light 
(\SI{500}{\nano\meter} - \SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The UV and VIS+IR spectra were merged 
in Opus software. % included in the spectrometer. 
\Gls{xrd} spectra were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer. 
All \gls{xrd} spectra were taken at \SI{5}{\degree} incident angle and compared to the internal database.

The \gls{iv} curves were measured with Agilent 4156C Precision Semiconductor 
Parameter Analyzer from \SI{-0.5}{\volt} to \SI{0.5}{\volt} with steps of 
\SI{10}{\milli\volt}.
Prior to \gls{iv} measurements the samples were sputtered with aluminium 
through a mask to produce a multitude of equidistant contacts with a Leybold 
UNIVEX450C Sputter System.
Directional current sputtering was used with Argon as inert gas at \SI{0.005}{\milli\bar} 
and with a power of \SI{40}{\watt} for \SI{700}{\second}.
Between sputtering and \gls{iv} measurements 
direct contacts to the steel substrate were created by removing a patch the \gls{zro}
layer with 
sand paper on two opposing edges of a sample and then by applying silver paste.
See figure~\ref{fig:circuit} for a sketch of the connectivity.

@@

@@

The then current procedure resulted in clear and continuous films, but was plagued from 

@@

allowed to hold the sample in place through underpressure and simultaneously heat it to a certain 

@@

relative concentration of Zr $c_{Zr}$, number of layers $n_{l}$, calcination temperature $T_{cal}$[\oc{}], heating rate $v_{cal}$[\oc{}/\h{}], \gls{db} velocity $v_{DB}$[\mm{}/\s{}] and \gls{db} temperature $T_{DB}$[\oc{}], respectively. 
After testing the first samples, the lower limit for \gls{db} velocities was altered from 0.1 to 1 (see table \ref{tab:pre-opt1}).
\begin{table}[hbt]

@@

	\caption{Pre-optimization experiments}

@@

			$c_{Zr}$	&$n_l$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\

@@

			$c_{Zr}$	&$n_l$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
	%conc	&layers	&$v_{\textrm{DB}}$	&$T_{\textrm{DB}}$	&$v_{\textrm{cal}}$	&$T_{\textrm{cal}}$		\\

@@

	4*	&6	&14	&60	&240	&500	\\
	4*	&6	&14	&60	&240	&500	\\
	4*	&6	&14	&60	&240	&500	\\

@@

%			\multicolumn{6}{c}{*different stabilisation reagent compositions}\\

@@

@@

%$T_{DB}$[\oc{}]
%$v_{DB}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a DB machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Shortly before the \gls{pso} the stabilisation agent was changed from \gls{acoh} to 
\gls{ipo} because of much better solution stability.
The up to this moment best process was chosen to be tested with \ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
%\td{As the sample showed the best all ex were proceeded with ipo as stabilatin agent. }
The sample produced with \gls{ipo} as stabilization agent showed comparable passivation results and better stability. Therefore \gls{ipo} was used  as stabilisation in further experiments.
After 
%a fitting recipe was found and 
the boundaries were fixed the process variables to 
produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
See table \ref{tab:space} for the space spanned for the optimisation.
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{Zr}$	&$n_l$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
